A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-07-17 Manuscript/PNAS-Adams-01.Rmd
vsn 1

For $\lambda$, deriving an effect size is more challenging, as $\lambda$ does not have a sampling distribution from which the standard error and confidence intervals may be obtained. Confidence intervals are therefore generated for the values of $\lambda$ that intersect the log-likehihood profile for corresponding percentiles of the $\chi^2$ distribution used to compare the putative model to a null model with $\lambda = 0$ [**add ref: MLC thinks Boettiger paper?**]. Thus, an effect size for $\lambda$ may be found as:

>>>>

For $\lambda$, deriving an effect size is more challenging, as $\lambda$ does not have a sampling distribution from which the standard error and confidence intervals may be obtained, and estimates from the Hessian matrix from PGLS are unreliable [@Boettiger_et_al2012]. Confidence intervals are therefore generated for the values of $\lambda$ that intersect the log-likehihood profile for corresponding percentiles of the $\chi^2$ distribution used to compare the putative model to a null model with $\lambda = 0$ [**add ref: MLC thinks Boettiger paper?**]. Thus, an effect size for $\lambda$ may be found as:
